### 2017-08-18 doc/MSI.tex
adding MSI User's Guide in doc folder

\documentclass[11pt]{article}  % include bezier curves
\renewcommand\baselinestretch{1.0}           % single space
%\pagestyle{empty}                            % no headers and page numbers
\author{}
\title{}

\oddsidemargin -10 true pt      % Left margin on odd-numbered pages.
\evensidemargin 10 true pt      % Left margin on even-numbered pages.
\marginparwidth 1.5 true in    % Width of marginal notes.
\oddsidemargin  0 true in       % Note that \oddsidemargin=\evensidemargin
\evensidemargin 0 true in
\topmargin -0.5 true in        % Nominal distance from top of page to top of
\textheight 9.0 true in         % Height of text (including footnotes and figures)
\textwidth 6.5 true in        % Width of text line.
\parindent=0pt                  % Do not indent paragraphs
\parskip=0.15 true in
%\usepackage{color}              % Need the color package

\usepackage[pdftex]{color, graphicx}
%\usepackage{graphicx} %for epsfig
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{latexsym}
\usepackage{mathrsfs}
\usepackage{eufrak}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{url}
\usepackage{hyperref}
\usepackage[pdftex]{color, graphicx}
%\usepackage{graphicx} %for epsfig
\usepackage{setspace}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{afterpage}
\usepackage{pdfpages}
\usepackage{tikz}
%\usepackage[lined,algonl,boxed]{algorithm2e}
%\renewcommand{\listalgorithmcfname}{LIST OF ALGORITHMS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{The MSI User's Guide}

\author{-- VERSION 0.1 --\\
\\
Scientific Computation Research Center \\
Rensselaer Polytechnic Institute}

\begin{document}

\maketitle

\newpage

\newpage
***************     SCOREC 3-CLAUSE BSD LICENSE     ***************
\\
\\
Copyright (c) 2017, Scientific Computation Research Center (SCOREC), Rensselaer Polytechnic Institute (RPI). All rights reserved.
\newline
\newline
Redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met:

\begin{itemize}
\item Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.

\item Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.

\item Neither the name of the SCOREC, RPI nor the names of its contributors may be used to endorse or promote products derived from this software without specific prior written permission.
\end{itemize}

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS ``AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
\newline
\newline
Questions to seols@rpi.edu\\
Derived from the OSI 3-clause BSD
\newpage
\newpage

\tableofcontents
\newpage
\include{msi-api}

%installation
\section{Installation}

MSI is a free open source software available in \url{https://github.com/SCOREC/msi}. 
This section discuss the S/W requirements and compilation briefly.

\subsection{S/W Requirements}

At a minumum, the following softwares are required to install MSI.
\begin{itemize}
\item \texttt{cmake} - v3.0 or higher
\item \texttt{MPI}
\item \texttt{Zoltan}~\cite{ZoltanOverviewArticle2002}
\item \texttt{PUMI}~\cite{pumi16, pumiweb}
\item \texttt{METIS/ParMETIS} ~\cite{ParmetisOverviewArticle2002}
\end{itemize}

The detailed discussion on how to build PUMI can be found in \emph{https://github.com/SCOREC/core/wiki/General-Build-instructions}.

\subsection{Compilation}

To build MSI, run a cmake configuration file and do \emph{``make install"}. Two example cmake configuration files are available in the top source folder;\emph{``openmpi-gcc4.4.5-real-config.sh"} for real type and \emph{``openmpi-gcc4.4.5-complex-config.sh"} for complex type.

The essential configuration options include:

\begin{itemize}
\item \texttt{ZOLTAN$\_$LIBRARY}: path and file name of Zoltan library
\item \texttt{PARMETIS$\_$LIBRARY}: path and file name of ParMETIS library
\item \texttt{METIS$\_$LIBRARY}: path and file name of METIS library
\item \texttt{SCOREC$\_$INCLUDE$\_$DIR}: path to PUMI header files
\item \texttt{SCOREC$\_$LIB$\_$DIR}: path and file name of PUMI libraries
\item \texttt{ENABLE$\_$PETSC}: set \texttt{ON} to link MSI with PETSc solver
\item \texttt{PETSC$\_$INCLUDE$\_$DIR}: path to PETSc header files
\item \texttt{PETSC$\_$LIB$\_$DIR}: path to PETSc libraries
\item \texttt{ENABLE$\_$TRILINOS}: set \texttt{ON} to link MSI with Trilinos solver
\item \texttt{TRILINOS$\_$INCLUDE$\_$DIR}: path to Trilinos header files
\item \texttt{TRILINOS$\_$LIB$\_$DIR}: path to Trilinos libraries
\item \texttt{DENABLE$\_$COMPLEX}: set \texttt{ON} to build MSI complex value
\item \texttt{CMAKE$\_$INSTALL$\_$PREFIX}: path to install MSI header file and library
\end{itemize}

In the current version, Trilinos is not supported.

For a complete list of configuration options, see \emph{``CMakeLists.txt"} in the top source folder.

\subsection{Test Program}
A test program with PETSc is available in \emph{``test/petsc/main.cc"} in the top source folder.
The test program is a good start to learn how to use MSI API. The input arguments of the test program are the following:
\begin{itemize}
\item \texttt{argv[1]} - input model file (.dmg)
\item \texttt{argv[2]} - input mesh file (.smb)
\end{itemize}

How to generate PUMI-readable model and mesh files and how to use PUMI are beyond the scope of this document. For such a topic, see PUMI User's Guide available in \url{http://www.scorec.rpi.edu/pumi}.

% Bibliography
\bibliographystyle{plain}
\bibliography{seol}
\end{document}

### 2017-08-18 doc/msi-api.tex
adding MSI User's Guide in doc folder

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{API Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The MSI API's are provided in the file \texttt{``msi.h"}. Throughout this section, unless specified, DOF, matrix row and column ID's are specified by a global ID.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Naming Convention}

MSI API function name consists of three words connected with `$\_$'.

\begin{itemize}
\item the first word is ``msi"
\item the second word is an operation target. If the operation target is system-wide, the operation target is ommited. For instance, the function name which initializes the MSI service consists of two words: \emph{msi}$\_$\emph{start}.
\item the third word is the operation description starting with a verb. For example, the function \emph{msi}$\_$\emph{matrix}$\_$\emph{getNumIter} returns the number of iterations in the solve operation. 
\end{itemize}

The following are operation targets used in the second word.

\begin{itemize}
\item \textit{field}: the api is performed on a field object
\item \textit{matrix}: the api is performed on a Petsc matrix
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Abbreviation}

Abbreviations may be used in API naming. See \textit{http://scorec.rpi.edu/wiki/Abbriviations} for more information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data Types and Classes}

For a geometry, partition and mesh model, the term \emph{instance} is used to indicate the model data existing on each process. For example, a mesh instance on process \emph{i} means a pointer to a mesh data structure on process \emph{i}, in which all mesh entities on process \emph{i} are contained and from which they are accessible. For all other data such as field and matrix, the term \emph{handle} is used to indicate the pointer to the data. For example, a matrix handle means a pointer to the matrix. The predefined data type has a prefix \emph{p} to indicate the pointer data type.

The following are predefined data types used in the interface function parameters.

\begin{tabular}{lp{14cm}}	
	pField & 	a field handle (defined in \texttt{``pumi.h"})\\
	pOwnership & 	a user-defined ownership handle (defined in \texttt{``pumi.h"}) \\
 	pMatrix &	a matrix handle \\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enumeration Types}

The enumeration type for matrix type is:

\begin{verbatim}
    msi_matrix_type {
        MSI_MULTIPLY = 0 /* matrix for multiplication */,
        MSI_SOLVE      	 /* 1 - matrix for solve */
    }
\end{verbatim}\vspace{-1cm}\hspace{1cm}

The enumeration type for matrix status is:

\begin{verbatim}
    msi_matrix_status {
        MSI_NOT_FIXED = 0 /* matrix is modifiable */,
        MSI_FIXED         /* 1 - matrix is not modifiable */
    }
\end{verbatim}\vspace{-1cm}\hspace{1cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{API Functions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Initialization and Finalization}

The functions initialize/finalize the MSI operations.

\begin{verbatim}
void msi_start(
    pMesh  /* in */  m, 
    pOwnership  /* in */  o=NULL)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a mesh and ownership handle, initialize MSI services for solver-PUMI interactions. If the ownership is not provided, the default is set to $NULL$. If the ownership is $NULL$, the PUMI's default ownership rule is used (a part with the minimum process rank is the owning part of duplicate copies).

Note that the following operations should be performed prior to this function.
\begin{itemize}
\item MPI initialization
\item Solver initialization (e.g. PetscInitialize)
\item PUMI initialization 
\item model and mesh loading
\end{itemize}

\begin{verbatim}
int msi_scorec_finalize()
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Finalize the MSI services and clears all internal data. Note that the following operations should follow to complete further finalizations.
\begin{itemize}
\item mesh deletion
\item PUMI finalization
\item Solver finalization (e.g. PetscFinalize)
\item MPI finalization
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Field}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{verbatim}
pField msi_field_create (
    pMesh  /* in */  m,
    const char*  /* in */  field_name, 
    int  /* in */  nv, 
    int  /* in */  nd)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given field name, the number of values ($nv$), and the number of DOF's per value ($nd$), create a field for all nodes (owned, non-owned part boundary and ghost). Note that PUMI allocates contiguous memory for the array of field data. The size of field data is \textit{nv}$*$\textit{st}$*$\textit{nd}$*$\textit{nn}, where \textit{st} is scalar type (1 for real, 2 for complex), and \textit{nn} is the number of local nodes on each process.

In terms of field operation, MSI provides the field creation only as PUMI field creation routine, \texttt{pumi$\_$field$\_$create}, does not support \textit{multiple values}. For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}. If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PETSc Matrix and Solver}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{verbatim}
pMatrix msi_matrix_create (
        int  /* in */  matrix_type,
        pField  /* in */  field)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix type and a field handle, create a matrix and return its handle. The matrix type indicates the purpose of the matrix: 0 for matrix-vector multiplication and 1 for solver. The input field handle is used to retrieve the numbering (row/column ID) for matrix manipulation. The status of matrix is \textit{MSI$\_$NOT$\_$FIXED} so the matrix values can be modified.

\begin{verbatim}
void msi_matrix_delete (pMatrix  /* in */  matrix)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, delete the matrix.

\begin{verbatim}
void msi_matrix_assemble (pMatrix  /* in */  matrix)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, perform matrix assembly and set the status of matrix  to \textit{MSI$\_$FIXED}. 
The matrix values cannot be modified any further.

\begin{verbatim}
void msi_matrix_insert (
    pMatrix  /* in */  matrix, 
    int  /* in */  row, 
    int  /* in */  column, 
    int  /* in */  scalar_type,
    double*  /* in */  value)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Insert or overwrite \textit{value} to the matrix at (\textit{row},\textit{column}).
\textit{row} and \textit{column} are global DOF ID associated with the matrix.
If \textit{value} is a real number, \textit{scalar$\_$type} is 0. Otherwise, \textit{scalar$\_$type} is 1. A real type value can be inserted into a complex matrix but a complex type value cannot be inserted into a real matrix.

\begin{verbatim}
void msi_matrix_add (
    pMatrix  /* in */  matrix, 
    int  /* in */  row, 
    int  /* in */  column, 
    int  /* in */  scalar_type,
    double*  /* in */  value)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Add \textit{value} to the existing value of matrix at (\textit{row},\textit{column}).
\textit{row} and \textit{column} are global DOF ID associated with the matrix.
If \textit{value} is a real number, \textit{scalar$\_$type} is 0. Otherwise, \textit{scalar$\_$type} is 1. A real type value can be inserted into a complex matrix but a complex type value cannot be inserted into a real matrix.

\begin{verbatim}
void msi_matrix_addBlock (
    pMatrix  /* in */  matrix, 
    int  /* in */  elm_id, 
    int  /* in */  row_index, 
    int  /* in */  column_index, 
    double*  /* in */  values)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, a local element ID, row variable index, colume variable index and an array of values, add values to the matrix corresponding to the nodes of the element.

\begin{verbatim}
void msi_matrix_setBC (
    pMatrix  /* in */  matrix, 
    int  /* in */  local_row_index)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle and a local row index, zero out all off-diagonal values in the row of the matrix and set the diagonal value to one. The operation is carried out during finalizing the matrix. It will overwrite other insertion operations to the local row of the matrix. For complex-valued matrix, the real part of the diagonal is set to one and the imaginary part is set to zero.
This function should be called on all processes that use the DOF numbering associated with the matrix row.

\begin{verbatim}
void msi_matrix_setLaplaceBC (
    pMatrix  /* in */  matrix, 
    int  /* in */  row, 
    int  /* in */  size, 
    int*  /* in */  columns, 
    double*  /* in */  values)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, a local row index, the  number of values to be inserted (\textit{size}), the columns to set the values (\textit{columns}), and the values to be set in the order of the \textit{columns}, set multiple values for the row of the matrix. If real values are inserted into a complex matrix, the corresponding imaginary parts are set to zero. The operation is carried out during finalizing the matrix. 
This function will overwrite other insertion operations to the row. This function should be called on all processes that use the DOF numbering associated with the matrix row.

\begin{verbatim}
void msi_matrix_multiply (
    pMatrix  /* in */  A, 
    pField  /* in */   x, 
    pField  /* out */  b)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle ($A$) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax"} and write the result in the field $b$. If the input matrix or the input field is complex-valued, the output field must be complex-valued.

\begin{verbatim}
void msi_matrix_solve (
        pMatrix  /* in */   A, 
        pField   /* in */   b, 
        pField   /* out */  x)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle ($A$) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b"} and write the solution into the field $x$.

\begin{verbatim}
int msi_matrix_getNumIter (pMatrix  /* in */  matrix)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, return the number of iterations of solver operation.

\begin{verbatim}
void msi_matrix_print(pMatrix  /* in */  matrix)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, print the $non$-$zero$ matrix value along with global row/colume index. The row/column ID starts with 0. PUMI provides an equivalent API for fields and nodes.

\begin{verbatim}
void msi_matrix_write (
    pMatrix  /* in */  matrix, 
    const char*  /* in */  file_name, 
    int  /* in */  start_index=0)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, file name and a starting local ID for nodes (default is 0), write the $non$-$zero$ matrix values in file(s). For each process \textit{i}, the matrix information is written in \texttt{``filename-i"}. If \textit{file$\_$name} is \textit{NULL}, \texttt{msi$\_$matrix$\_$print} is performed.
PUMI provides an equivalent API for fields and nodes.

### 2017-08-18 api/msi.cc

@@ -19,6 +19,8 @@ using std::vector;
 
 extern pOwnership msi_ownership=NULL;
 
+void set_adj_node_tag(pMeshTag num_global_adj_node_tag, pMeshTag num_own_adj_node_tag);
+
 // Error if serial mesh is loaded and partitioned as pumi_ment_getID(e) is not sequential
 void msi_ment_getLocalFieldID(pMeshEnt e, pField f, int* start_dof_id, int* end_dof_id_plus_one)
 {
@@ -312,18 +314,20 @@ void msi_start(pMesh m, pOwnership o)
   msi_ownership=o;
   pumi_mesh_setCount(m, o);
   pumi_mesh_createGlobalID(m, o);
+
+  PetscMemorySetGetMaximumUsage();
+  msi_solver::instance()->num_global_adj_node_tag = pumi::instance()->mesh->createIntTag("msi_num_global_adj_node", 1);
+  msi_solver::instance()->num_own_adj_node_tag = pumi::instance()->mesh->createIntTag("msi_num_own_adj_node", 1);
+  set_adj_node_tag(msi_solver::instance()->num_global_adj_node_tag, msi_solver::instance()->num_own_adj_node_tag);
+
 }
 
 void msi_finalize(pMesh m)
 {  
-  typedef std::map<int, msi_matrix*> matrix_container_map;
-  for (std::map<int, msi_matrix*>::iterator it=msi_solver::instance()->matrix_container->begin();
-      it!=msi_solver::instance()->matrix_container->end(); ++it)
-  {
-    if(!PCU_Comm_Self()) std::cout<<"[MSI INFO] "<<__func__<<": matrix "<<it->first<<" deleted\n";
-    delete it->second;
-  }
-  msi_solver::instance()->matrix_container->clear();
+  apf::removeTagFromDimension(m, msi_solver::instance()->num_global_adj_node_tag, 0);
+  m->destroyTag(msi_solver::instance()->num_global_adj_node_tag);
+  apf::removeTagFromDimension(m, msi_solver::instance()->num_own_adj_node_tag, 0);
+  m->destroyTag(msi_solver::instance()->num_own_adj_node_tag);
 
   while(m->countFields())
   {
@@ -358,14 +362,14 @@ void msi_field_assign(pField f, double* fac)
 }
 
 
-pField msi_field_create (const char* /* in */ field_name, int /*in*/ num_values, int /*in*/ num_dofs_per_value)
[…]

### 2017-08-18 api/msi.h

@@ -19,15 +19,16 @@
 enum msi_matrix_type { /*0*/ MSI_MULTIPLY=0, 
                        /*1*/ MSI_SOLVE}; 
 enum msi_matrix_status { /*0*/ MSI_NOT_FIXED=0,
-                         /*2*/ MSI_FIXED};
+                         /*1*/ MSI_FIXED};
 
 // START OF API
 // remember to delete ownership after use
-void msi_start(pMesh m, pOwnership o);
+void msi_start(pMesh m, pOwnership o=NULL);
 void msi_finalize(pMesh m);
 
-pField msi_field_create (const char* /* in */ field_name, 
-                      int /*in*/ num_values, int /*in*/ num_dofs_per_value);
+// field creation with multiple variables
+pField msi_field_create (pMesh m, const char* /* in */ field_name, 
+                      int /*in*/ nv, int /*in*/ nd);
 
 #ifdef MSI_PETSC
 #include "msi_petsc.h"
@@ -35,23 +36,22 @@ class msi_matrix;
 typedef msi_matrix* pMatrix;
 /** matrix and solver functions with PETSc */
 pMatrix msi_matrix_create(int matrix_type, pField f);
-void msi_matrix_freeze(pMatrix mat);
 void msi_matrix_delete(pMatrix mat);
+void msi_matrix_assemble(pMatrix mat);
 
-void msi_matrix_insert(pMatrix mat, int row, int column, double* val);
-void msi_matrix_add(pMatrix mat, int row, int column, double* val);
+void msi_matrix_insert(pMatrix mat, int row, int column, int scalar_type, double* val);
+void msi_matrix_add(pMatrix mat, int row, int column, int scalar_type, double* val);
 void msi_matrix_addBlock(pMatrix mat, int ielm, int rowVarIdx, int columnVarIdx, double* values);
 
-void msi_matrix_setBC(pMatrix matd, int row);
-void msi_matrix_setLaplaceBC (pMatrix mat, int row, int numVals, int* columns, double* values);
+void msi_matrix_setBC(pMatrix mat, int row);
+void msi_matrix_setLaplaceBC (pMatrix mat, int row, int size, int* columns, double* values);
 
 void msi_matrix_solve(pMatrix mat, pField rhs, pField sol);
 int msi_matrix_getNumIter(pMatrix mat);
 void msi_matrix_multiply(pMatrix mat, pField inputvec, pField outputvec);
 
 // auxiliary
[…]

### 2017-08-18 openmpi-gcc4.4.5-real-config.sh

@@ -10,8 +10,6 @@ cmake .. \
   -DCMAKE_Fortran_FLAGS="-fpic "\
   -DSCOREC_INCLUDE_DIR=$PREFIX/include \
   -DSCOREC_LIB_DIR=$PREFIX/lib \
-  -DMSI_INCLUDE_DIR=$PREFIX/include \
-  -DMSI_LIB_DIR=$PREFIX/lib \
   -DZOLTAN_LIBRARY="$PREFIX/lib/libzoltan.a" \
   -DPARMETIS_LIBRARY="$PETSC_DIR/$PETSC_ARCH/lib/libparmetis.a" \
   -DMETIS_LIBRARY="$PETSC_DIR/$PETSC_ARCH/lib/libmetis.a" \

### 2017-08-18 src/msi_solver.cc

@@ -38,153 +38,14 @@ msi_solver* msi_solver::instance()
   return _instance;
 }
 
-struct entMsg
-{
-  int pid;
-  apf::MeshEntity* ent;
-  entMsg( int pid_p=0, apf::MeshEntity* ent_p=NULL)
-  {
-    pid=pid_p;
-    ent=ent_p;
-  }
-};
-
-struct classcomp
-{
-  bool operator() (const entMsg& lhs, const entMsg& rhs) const
-  {
-    if(lhs.ent==rhs.ent) return lhs.pid<rhs.pid;
-    else return lhs.ent<rhs.ent;
-  }
-};
-
-
-// **********************************************
-void set_adj_node_tag(pMeshTag num_global_adj_node_tag, pMeshTag num_own_adj_node_tag)
-// **********************************************
-{
-  pMesh mesh = pumi::instance()->mesh;
-
-  int value;
-  int brgType = mesh->getDimension()-1;
-
-  apf::MeshEntity* e;
-  apf::MeshIterator* it = mesh->begin(0);
-  PCU_Comm_Begin();
-  while ((e = mesh->iterate(it)))
-  {
-    int num_adj_node=0;
-    apf::Adjacent elements;
-    apf::getBridgeAdjacent(mesh, e, brgType, 0, elements);
-    int num_adj = elements.getSize();
-
-    for (int i=0; i<num_adj; ++i)
-    {
-      if (pumi_ment_isOwned(elements[i]))
-        ++num_adj_node;
-    }
-    mesh->setIntTag(e, num_own_adj_node_tag, &num_adj_node);
-
-    if (!mesh->isShared(e)) continue;
-    // first pass msg size to owner
-    int own_partid = pumi_ment_getOwnPID(e);
-    apf::MeshEntity* own_copy = pumi_ment_getOwnEnt(e);
-
-    if (own_partid==PCU_Comm_Self()) continue;
-    PCU_COMM_PACK(own_partid, own_copy);
-    PCU_Comm_Pack(own_partid, &num_adj,sizeof(int));
-  }
-  mesh->end(it);
-
-  PCU_Comm_Send();
-
-  std::map<apf::MeshEntity*, std::map<int, int> > count_map;
-  while (PCU_Comm_Listen())
-  {
-    while ( ! PCU_Comm_Unpacked())
-    {
-      PCU_COMM_UNPACK(e);
-      PCU_Comm_Unpack(&value,sizeof(int));
[…]

### 2017-08-18 test/petsc/main.cc

@@ -78,9 +78,9 @@ int main( int argc, char** argv)
   if (mesh_dim==3) nd=12;
 
   if(!PCU_Comm_Self()) cout<<"* creating fields - "<<nv*nd<<" DOFs per node\n";
-  pField b_field = msi_field_create ("b_field", nv, nd);
-  pField c_field = msi_field_create ("c_field", nv, nd);
-  pField x_field = msi_field_create ("x_field", nv, nd);
+  pField b_field = msi_field_create (m, "b_field", nv, nd);
+  pField c_field = msi_field_create (m, "c_field", nv, nd);
+  pField x_field = msi_field_create (m, "x_field", nv, nd);
 
   pMeshEnt e = pumi_mesh_findEnt(m, mesh_dim, 0);
   int num_nodes_elem = pumi_ment_getNumAdj(e, 0);
@@ -153,8 +153,8 @@ int main( int argc, char** argv)
   t2 = MPI_Wtime();
 
   if(!PCU_Comm_Self()) cout<<"* assemble matrix ..."<<endl;
-  msi_matrix_freeze(matrix_mult);
-  msi_matrix_freeze(matrix_solve); 
+  msi_matrix_assemble(matrix_mult);
+  msi_matrix_assemble(matrix_solve); 
   t3 = MPI_Wtime();
 
   if(!PCU_Comm_Self()) cout<<"* multiply Ab=c ..."<<endl;

### 2017-08-18 doc/msi-api.tex
adding API related DOF ID per mesh entity

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The MSI API's are provided in the file \texttt{``msi.h"}. Throughout this section, unless specified, DOF, matrix row and column ID's are specified by a global ID.
+The MSI API's are provided in the file \texttt{``msi.h"}.
+Throughout this section, unless specified, DOF, matrix row and column ID's are specified by a local ID.
+A word ``\emph{global}" in a function name indicates that the function involves global operation or global data.
 
@@
 \begin{tabular}{lp{14cm}}	
+	pMesh
+        pMeshEnt 
         pField & 	a field handle (defined in \texttt{``pumi.h"})\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Mesh Entity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In terms of mesh entity operation, MSI provides the operations only related to field ID of individual mesh entity as those are not supported in PUMI.
+For the rest of mesh entity operations including setting/getting field data (DOF) over nodes, use the API's in \texttt{PUMI.h}.
+
+\begin{verbatim}
+void msi_ment_getFieldID (
+    pMeshEnt  /* in */  e, 
+    pField  /* in */  f, 
+    int  /* in */  i,
+    int*  /* out */  start_dof_id, 
+    int*  /* out */  end_dof_id_plus_one)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a mesh entity handle, field handle and the index of node $i$, return the starting local ID and the ending local ID plus one for field data (DOF) of $i^{th}$ node of the entity.
+
+\begin{verbatim}
+void msi_ment_getGlobalFieldID (
+    pMeshEnt  /* in */  e, 
+    pField  /* in */  f, 
+    int  /* in */  i,
+    int*  /* out */  start_dof_id, 
+    int*  /* out */  end_dof_id_plus_one)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a mesh entity handle, field handle and the index of node $i$, return the starting global ID and the ending global ID plus one for field data (DOF) of $i^{th}$ node of the mesh entity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Field}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In terms of field operation, MSI provides the field creation only as PUMI field creation routine, \texttt{pumi$\_$field$\_$create}, does not support \textit{multiple values}.
+For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}.
+If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.
 
@@
 The size of field data is \textit{nv}$*$\textit{st}$*$\textit{nd}$*$\textit{nn}, where \textit{st} is scalar type (1 for real, 2 for complex), and \textit{nn} is the number of local nodes on each process.
-
-In terms of field operation, MSI provides the field creation only as PUMI field creation routine, \texttt{pumi$\_$field$\_$create}, does not support \textit{multiple values}.
-For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}.
-If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.
 
@@
     pMatrix  /* in */  matrix, 
-    int  /* in */  row, 
-    int  /* in */  column, 
+    int  /* in */  r, 
+    int  /* in */  c, 
     int  /* in */  scalar_type,
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Insert or overwrite \textit{value} to the matrix at (\textit{row},\textit{column}).
-\textit{row} and \textit{column} are global DOF ID associated with the matrix.
+Given a matrix handle, local DOF ID $r$ and $c$, scalar type (0 for real, 1 for complex) and an array of double values, insert or overwrite \textit{value} to the matrix at (\textit{r},\textit{c}).
 If \textit{value} is a real number, \textit{scalar$\_$type} is 0.
@@
 
+If the number of DOF's associated with the field is $d$, $r$ or $c$ divided by $d$ is a local ID of corresponding mesh entity.
+Use \texttt{msi$\_$ment$\_$getFieldID} to get local DOF ID of a mesh entity.
+
 \begin{verbatim}
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Add \textit{value} to the existing value of matrix at (\textit{row},\textit{column}).
-\textit{row} and \textit{column} are global DOF ID associated with the matrix.
+Given a matrix handle, local DOF ID $r$ and $c$, scalar type (0 for real, 1 for complex) and an array of double values, add \textit{value} to the existing value of matrix at (\textit{r},\textit{c}).
 If \textit{value} is a real number, \textit{scalar$\_$type} is 0.
 Otherwise, \textit{scalar$\_$type} is 1.
-A real type value can be inserted into a complex matrix but a complex type value cannot be inserted into a real matrix.
+A real type value can be added into a complex matrix but a complex type value cannot be added into a real matrix.
+
+If the number of DOF's associated with the field is $d$, $r$ or $c$ divided by $d$ is a local ID of corresponding mesh entity.
+Use \texttt{msi$\_$ment$\_$getFieldID} to get local DOF ID of a mesh entity.
 
@@
     pMatrix  /* in */  matrix, 
-    int  /* in */  elm_id, 
-    int  /* in */  row_index, 
-    int  /* in */  column_index, 
+    int  /* in */  elem_id, 
+    int  /* in */  r_value_index, 
+    int  /* in */  c_value_index, 
     double*  /* in */  values)
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle, a local element ID, row variable index, colume variable index and an array of values, add values to the matrix corresponding to the nodes of the element.
+Given a matrix handle, a local element ID, row value index, column value index, and a double array containing element matrix values, add values in the element matrix to the global matrix.
+The the number of the values associated with the field is 1, accepted value for \textit{r$\_$value$\_$index} and \textit{c$\_$value$\_$index} is 0.
 
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle and a local row index, zero out all off-diagonal values in the row of the matrix and set the diagonal value to one.
+Given a matrix handle of type 1 (\textit{MSI$\_$SOLVE}) and a local row index, zero out all off-diagonal values in the row of the matrix and set the diagonal value to one.
 The operation is carried out during finalizing the matrix.
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle, a local row index, the  number of values to be inserted (\textit{size}), the columns to set the values (\textit{columns}), and the values to be set in the order of the \textit{columns}, set multiple values for the row of the matrix.
+Given a matrix handle of type 1 (\textit{MSI$\_$SOLVE}), a local row index, the  number of values to be inserted (\textit{size}), the columns to set the values (\textit{columns}), and the values to be set in the order of the \textit{columns}, set multiple values for the row of the matrix.
 If real values are inserted into a complex matrix, the corresponding imaginary parts are set to zero.
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle ($A$) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax"} and write the result in the field $b$.
+Given a matrix handle ($A$) of type 0 (\textit{MSI$\_$MULTIPLY}) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax"} and write the result in the field $b$.
 If the input matrix or the input field is complex-valued, the output field must be complex-valued.
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle ($A$) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b"} and write the solution into the field $x$.
+Given a matrix handle ($A$) of type 1 (\textit{MSI$\_$SOLVE}) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b"} and write the solution into the field $x$.
 
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle, return the number of iterations of solver operation.
+Given a matrix handle of type 1 (\textit{MSI$\_$SOLVE}), return the number of iterations of solve operation.
 

### 2017-08-18 api/msi.cc

@@ -21,16 +21,68 @@ extern pOwnership msi_ownership=NULL;
 
 void set_adj_node_tag(pMeshTag num_global_adj_node_tag, pMeshTag num_own_adj_node_tag);
 
-// Error if serial mesh is loaded and partitioned as pumi_ment_getID(e) is not sequential
-void msi_ment_getLocalFieldID(pMeshEnt e, pField f, int* start_dof_id, int* end_dof_id_plus_one)
+//*******************************************************
+void msi_ment_getFieldID (pMeshEnt e, pField f, int inode,
+     int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
+//*******************************************************
 {
   int num_dof = apf::countComponents(f);
 #ifdef PETSC_USE_COMPLEX
   num_dof/=2;
 #endif
-  *start_dof_id = pumi_ment_getID(e)*num_dof;
-  *end_dof_id_plus_one = *start_dof_id + num_dof;
+  // FIXME: replace getMdsIndex with numbering
+  int ent_id = getMdsIndex(pumi::instance()->mesh, e);
+  *start_dof_id = ent_id*num_dof;
+  *end_dof_id_plus_one = *start_dof_id +num_dof;
 }
+
+// internal function
+//*******************************************************
+int msi_ent_getlocaldofid(int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
+                       int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
+//*******************************************************
+{
+  if (*ent_dim!=0)
+    return MSI_FAILURE;
+
+  apf::MeshEntity* e =getMdsEntity(pumi::instance()->mesh, *ent_dim, *ent_id);
+  assert(e);
+
+  msi_ment_getFieldID(e, f, 0, start_dof_id, end_dof_id_plus_one);
+  return MSI_SUCCESS;
+}
+
+//*******************************************************
+void msi_ment_getGlobalFieldID (pMeshEnt e, pField f, int inode,
+     int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
+//*******************************************************
+{
+  int num_dof = apf::countComponents(f);
+#ifdef PETSC_USE_COMPLEX
+  num_dof/=2;
+#endif
[…]

### 2017-08-18 api/msi.h

@@ -26,6 +26,13 @@ enum msi_matrix_status { /*0*/ MSI_NOT_FIXED=0,
 void msi_start(pMesh m, pOwnership o=NULL);
 void msi_finalize(pMesh m);
 
+void msi_ment_getFieldID (pMeshEnt e, pField f, int inode,
+     int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
+
+void msi_ment_getGlobalFieldID (pMeshEnt e, pField f, int inode,
+     int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
+
+
 // field creation with multiple variables
 pField msi_field_create (pMesh m, const char* /* in */ field_name, 
                       int /*in*/ nv, int /*in*/ nd);

### 2017-08-18 doc/msi-api.tex
fixing minor errors in User's Guide

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The MSI API's are provided in the file \texttt{``msi.h"}.
+The MSI API's are provided in the file ``\texttt{msi.h}".
 Throughout this section, unless specified, DOF, matrix row and column ID's are specified by a local ID.
@@
 \begin{tabular}{lp{14cm}}	
-	pMesh
-        pMeshEnt 
-        pField & 	a field handle (defined in \texttt{``pumi.h"})\\
-	pOwnership & 	a user-defined ownership handle (defined in \texttt{``pumi.h"}) \\
+	pMesh  & 	a mesh instance (defined in ``\texttt{pumi.h}")\\
+        pMeshEnt & 	a mesh entity handle (defined in ``\texttt{pumi.h}")\\
+        pField & 	a field handle (defined in ``\texttt{pumi.h}")\\
+	pOwnership & 	a user-defined ownership handle (defined in ``\texttt{pumi.h}") \\
  	pMatrix &	a matrix handle \\
@@
 For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}.
-If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.
 
@@
 The size of field data is \textit{nv}$*$\textit{st}$*$\textit{nd}$*$\textit{nn}, where \textit{st} is scalar type (1 for real, 2 for complex), and \textit{nn} is the number of local nodes on each process.
+
+ If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.
 
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle ($A$) of type 0 (\textit{MSI$\_$MULTIPLY}) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax"} and write the result in the field $b$.
+Given a matrix handle ($A$) of type 0 (\textit{MSI$\_$MULTIPLY}) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax}" and write the result in the field $b$.
 If the input matrix or the input field is complex-valued, the output field must be complex-valued.
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix handle ($A$) of type 1 (\textit{MSI$\_$SOLVE}) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b"} and write the solution into the field $x$.
+Given a matrix handle ($A$) of type 1 (\textit{MSI$\_$SOLVE}) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b}" and write the solution into the field $x$.
 
@@
 Given a matrix handle, file name and a starting local ID for nodes (default is 0), write the $non$-$zero$ matrix values in file(s).
-For each process \textit{i}, the matrix information is written in \texttt{``filename-i"}.
+For each process \textit{i}, the matrix information is written in ``\texttt{filename-i}".
 If \textit{file$\_$name} is \textit{NULL}, \texttt{msi$\_$matrix$\_$print} is performed.

### 2017-08-22 doc/msi-api.tex
elaborating msi_field_create

@@
 
-In terms of field operation, MSI provides the field creation only as PUMI field creation routine, \texttt{pumi$\_$field$\_$create}, does not support \textit{multiple values}.
-For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}.
+In terms of PUMI field, the attributes include:
+\begin{itemize}
+\item field name: unique string 
+\item field size: the number of field data per node
+\item field type: \texttt{PUMI$\_$SCALAR} for a real number, \texttt{PUMI$\_$VECTOR} for real numbers of size 3, \texttt{PUMI$\_$MATRIX} for real numbers of size 9, and \texttt{PUMI$\_$PACKED} for real numbers of arbitrary size
+\item shape function to specify node distribution. The default shape is \textit{Linear} where nodes are associated only with vertices.
+\end{itemize}
+
+To support solver with advanced features, MSI supports the field API's with multiple field variables per node and complex number.
+If not specified here, use the field API's \texttt{PUMI.h} for the rest of field operations.
 
@@
     int  /* in */  nv, 
-    int  /* in */  nd)
+    int  /* in */  nd, 
+    pShape  /* in */  s=NULL)
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given field name, the number of values ($nv$), and the number of DOF's per value ($nd$), create a field for all nodes (owned, non-owned part boundary and ghost).
-Note that PUMI allocates contiguous memory for the array of field data.
-The size of field data is \textit{nv}$*$\textit{st}$*$\textit{nd}$*$\textit{nn}, where \textit{st} is scalar type (1 for real, 2 for complex), and \textit{nn} is the number of local nodes on each process.
+Given field name, the number of values per node ($nv$), the number of field data per value of node ($nd$), and a shape function, \emph{(i)} create a field for all nodes (owned, non-owned part boundary and ghost), \emph{(ii)} switch the memory space for field data to a contiguous array, and \emph{(iii)} initialize the field data.
+The \emph{size}, the number of field data per node is \textit{nv}$*$\textit{nd}.
+The size of contiguous array for each process is \textit{size}$*$\textit{nn} for real number and \textit{size}$*$\textit{nn}$*$2 for complex number, where \textit{nn} is the number of local nodes on each process.
+The field data type (real or complex) is determined at time of configuration.
+See Section~\ref{install} for how to configure MSI with complex number.
 
- If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.
+The field shape is optional and the default is \textit{NULL}. If it is \textit{NULL}, the field shape of the mesh is used (a field shape returned by \texttt{pumi$\_$mesh$\_$getShape}).
+
+ If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd, s)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd, PUMI$\_$PACKED, s)} followed by \texttt{pumi$\_$field$\_$freeze} and \texttt{pumi$\_$ment$\_$setField} with value $0$ for all nodes.
+
+\begin{verbatim}
+int msi_field_getNumVal (pField  /* in*/  f)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a field handle, return the number of value per node, \textit{nv}. If the field was created with \texttt{pumi$\_$field$\_$create}, return 1.
+
+\begin{verbatim}
+int msi_field_getSize (pField  /* in*/  f)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a field handle, return the field size, \textit{nv}$*$\textit{nd}.
 

### 2017-08-22 api/msi.cc

@@ -8,6 +8,7 @@
  
 *******************************************************************************/
 #include "msi.h"
+#include "msi_solver.h"
 #include "msi_petsc.h"
 #include <iostream>
 #include "PCU.h"
@@ -36,22 +37,6 @@ void msi_ment_getFieldID (pMeshEnt e, pField f, int inode,
   *end_dof_id_plus_one = *start_dof_id +num_dof;
 }
 
-// internal function
-//*******************************************************
-int msi_ent_getlocaldofid(int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
-                       int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
-//*******************************************************
-{
-  if (*ent_dim!=0)
-    return MSI_FAILURE;
-
-  apf::MeshEntity* e =getMdsEntity(pumi::instance()->mesh, *ent_dim, *ent_id);
-  assert(e);
-
-  msi_ment_getFieldID(e, f, 0, start_dof_id, end_dof_id_plus_one);
-  return MSI_SUCCESS;
-}
-
 //*******************************************************
 void msi_ment_getGlobalFieldID (pMeshEnt e, pField f, int inode,
      int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
@@ -67,231 +52,9 @@ void msi_ment_getGlobalFieldID (pMeshEnt e, pField f, int inode,
   *end_dof_id_plus_one = *start_dof_id +num_dof;
 }
 
-// internal function
 //*******************************************************
-int msi_ent_getglobaldofid (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
-         int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
-//*******************************************************
-{
-  if (*ent_dim!=0)
-    return MSI_FAILURE;
-
-  apf::MeshEntity* e =getMdsEntity(pumi::instance()->mesh, *ent_dim, *ent_id);
-  assert(e);
-
-  msi_ment_getGlobalFieldID(e, f, 0, start_dof_id, end_dof_id_plus_one);
-  return MSI_SUCCESS;
-}
-
-
-void msi_ment_getGlobalFieldID(pMeshEnt e, pField f, int* start_dof_id, int* end_dof_id_plus_one)
-{
-  int num_dof = apf::countComponents(f);
-#ifdef PETSC_USE_COMPLEX
-  num_dof/=2;
-#endif
[…]

### 2017-08-22 api/msi.h

@@ -35,12 +35,15 @@ void msi_ment_getGlobalFieldID (pMeshEnt e, pField f, int inode,
 
 // field creation with multiple variables
 pField msi_field_create (pMesh m, const char* /* in */ field_name, 
-                      int /*in*/ nv, int /*in*/ nd);
+                      int /*in*/ nv, int /*in*/ nd, pShape shape=NULL);
+int msi_field_getNumVal(pField f);
+int msi_field_getSize(pField f);
 
 #ifdef MSI_PETSC
 #include "msi_petsc.h"
 class msi_matrix;
 typedef msi_matrix* pMatrix;
+
 /** matrix and solver functions with PETSc */
 pMatrix msi_matrix_create(int matrix_type, pField f);
 void msi_matrix_delete(pMatrix mat);

### 2017-08-22 include/msi_petsc.h

@@ -8,40 +8,14 @@
  
 *******************************************************************************/
 #ifdef MSI_PETSC
-#ifndef MSI_SOLVER_H
-#define MSI_SOLVER_H
-//#include "superlu_ddefs.h" // gridinfo_t
-#include "apf.h"
+#ifndef MSI_PETSC_H
+#define MSI_PETSC_H
+#include "pumi.h"
 #include "petscksp.h"
-#include "apfNumbering.h"
 #include "msi.h"
+#include "msi_solver.h"
 #include <vector>
-
-// helper routines
-// helper routines
-pMeshEnt get_ent(pMesh mesh, int ent_dim, int ent_id);
-void msi_mesh_getnumownent (int* /* in*/ ent_dim, int* /* out */ num_ent);
-
-int msi_ent_getownpartid (int* /* in */ ent_dim, int* /* in */ ent_id, 
-                            int* /* out */ owning_partid);
-int msi_ent_getlocaldofid(int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
-                       int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
-int msi_ent_getglobaldofid (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
-         int* /* out */ start_global_dof_id, int* /* out */ end_global_dof_id_plus_one);
-
-int msi_ent_setdofdata (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
-                          int* /* out */ num_dof, double* dof_data);
-int msi_ent_getdofdata (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
-                          int* /* out */ num_dof, double* dof_data);
-
-int msi_field_getglobaldofid (pField f, 
-         int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
-void msi_field_getinfo(pField f, 
-     char* /* out*/ field_name, int* num_values, int* total_num_dof);
-int msi_field_getnumowndof (pField f, int* /* out */ num_own_dof);
-int msi_field_getdataptr (pField f, double** pts);
-int msi_field_getowndofid (pField f, 
-         int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
+#include <map>
 int copyField2PetscVec(pField f, Vec& petscVec);
[…]

### 2017-08-22 src/msi_petsc.cc

@@ -41,7 +41,7 @@ int matrix_solve::initialize()
   // initialize matrix
   setupMat();
   preAllocate();
-  if(!msi_solver::instance()->assembleOption) setUpRemoteAStruct();
+  setUpRemoteAStruct();
   int ierr = MatSetUp (*A); // "MatSetUp" sets up internal matrix data structure for the later use
   //disable error when preallocate not enough
   //check later
@@ -264,7 +264,7 @@ matrix_solve::~matrix_solve()
   if(kspSet)
     KSPDestroy(ksp);
   delete ksp;
-  if(mat_status==MSI_NOT_FIXED && msi_solver::instance()->assembleOption==0) MatDestroy(&remoteA);
+  if(mat_status==MSI_NOT_FIXED) MatDestroy(&remoteA);
 }
 
 int matrix_solve::assemble()
@@ -272,21 +272,19 @@ int matrix_solve::assemble()
   PetscErrorCode ierr;
   double t1 = MPI_Wtime(), t2=t1;
 
-  if(!msi_solver::instance()->assembleOption)
-  {
     ierr = MatAssemblyBegin(remoteA, MAT_FINAL_ASSEMBLY);
     CHKERRQ(ierr);
     ierr = MatAssemblyEnd(remoteA, MAT_FINAL_ASSEMBLY);
     t2 = MPI_Wtime();
     //pass remoteA to ownnering process
-    int brgType = 2;
+    int vertex_type=0, brgType = 2;
     if (pumi::instance()->mesh->getDimension()==3) brgType =3;
 
-    int dofPerVar = 6;
     char field_name[256];
-    int num_values, total_num_dof, vertex_type=0;
-    msi_field_getinfo(field, field_name, &num_values, &total_num_dof);
-    dofPerVar=total_num_dof/num_values;
+    int num_values = msi_field_getNumVal(field);
+    int total_num_dof = msi_field_getSize(field);
+
+    int dofPerVar=total_num_dof/num_values;
  
     int num_vtx = pumi_mesh_getNumEnt(pumi::instance()->mesh, 0);
     PetscInt firstRow, lastRowPlusOne;
@@ -426,7 +424,7 @@ int matrix_solve::assemble()
     }
     valuesRecvBuff.clear();
     idxRecvBuff.clear();
-  }
+
   ierr = MatAssemblyBegin(*A, MAT_FINAL_ASSEMBLY); 
   CHKERRQ(ierr);
[…]

### 2017-08-22 src/msi_solver.cc

@@ -9,9 +9,9 @@
 *******************************************************************************/
 #ifdef MSI_PETSC
 #include "msi.h"
-#include "msi_petsc.h"
+#include "msi_solver.h"
 #include "apf.h"
-#include "apfNumbering.h"
+#include "apfMDS.h"
 #include "apfShape.h"
 #include "apfMesh.h"
 #include <vector>
@@ -39,30 +39,222 @@ msi_solver* msi_solver::instance()
 }
 
 msi_solver::msi_solver()
-: assembleOption(0) 
 {
-  matrix_container = new std::map<int, msi_matrix*>;
+  field_container = new std::map<pField, int>;
 }
 
 msi_solver::~msi_solver()
 {
-  if (matrix_container!=NULL)
-    matrix_container->clear();
-  matrix_container=NULL;
+  if (field_container!=NULL)
+    field_container->clear();
+  field_container=NULL;
   delete _instance;
 }
 
-void msi_solver::add_matrix(int matrix_id, msi_matrix* matrix)
+void msi_solver::add_field(pField f, int n)
 {
-  assert(matrix_container->find(matrix_id)==matrix_container->end());
-  matrix_container->insert(std::map<int, msi_matrix*>::value_type(matrix_id, matrix));
+  assert(field_container->find(f)==field_container->end());
+  field_container->insert(std::map<pField, int>::value_type(f,n));
 }
 
-msi_matrix* msi_solver::get_matrix(int matrix_id)
+int msi_solver::get_num_value(pField f)
 {
-  std::map<int, msi_matrix*>::iterator mit = matrix_container->find(matrix_id);
-  if (mit == matrix_container->end()) 
-    return (msi_matrix*)NULL;
+  std::map<pField, int>::iterator mit = field_container->find(f);
+  if (mit == field_container->end()) 
+    return 0;
   return mit->second;
 }
+
+// helper routines
+
+
+// internal function
+//*******************************************************
+int msi_ent_getlocaldofid(int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
+                       int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one)
+//*******************************************************
+{
+  if (*ent_dim!=0)
+    return MSI_FAILURE;
+
[…]

### 2017-08-22 include/msi_solver.h
checking in a missing file

@@ -1,0 +1,64 @@
+/****************************************************************************** 
+
+  (c) 2017 Scientific Computation Research Center, 
+      Rensselaer Polytechnic Institute. All rights reserved.
+  
+  This work is open source software, licensed under the terms of the
+  BSD license as described in the LICENSE file in the top-level directory.
+ 
+*******************************************************************************/
+#ifndef MSI_SOLVER_H
+#define MSI_SOLVER_H
+#include "pumi.h"
+#include "msi.h"
+#include <map>
+
+// helper routines
+// helper routines
+pMeshEnt get_ent(pMesh mesh, int ent_dim, int ent_id);
+void msi_mesh_getnumownent (int* /* in*/ ent_dim, int* /* out */ num_ent);
+
+int msi_ent_getownpartid (int* /* in */ ent_dim, int* /* in */ ent_id, 
+                            int* /* out */ owning_partid);
+int msi_ent_getlocaldofid(int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
+                       int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
+int msi_ent_getglobaldofid (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
+         int* /* out */ start_global_dof_id, int* /* out */ end_global_dof_id_plus_one);
+
+int msi_ent_setdofdata (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
+                          int* /* out */ num_dof, double* dof_data);
+int msi_ent_getdofdata (int* /* in */ ent_dim, int* /* in */ ent_id, pField f, 
+                          int* /* out */ num_dof, double* dof_data);
+
+int msi_field_getglobaldofid (pField f, 
+         int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
+
+int msi_field_getNumVal(pField f);
+int msi_field_getNumDOF(pField f);
+int msi_field_getnumowndof (pField f, int* /* out */ num_own_dof);
+int msi_field_getdataptr (pField f, double** pts);
+int msi_field_getowndofid (pField f, 
+         int* /* out */ start_dof_id, int* /* out */ end_dof_id_plus_one);
+
+class msi_solver
+{
+public:
+  // functions
+  msi_solver();
+  ~msi_solver();
+  static msi_solver* instance();
+
+  // field 
+  int get_num_value(pField);
[…]

### 2017-09-14 doc/msi-api.tex
checking in a missing file
adding msi_matrix_getField

@@
     pMesh  /* in */  m, 
-    pOwnership  /* in */  o=NULL)
+    pOwnership  /* in */  o=NULL, 
+    pShape  /* in */  s=NULL)
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a mesh and ownership handle, initialize MSI services for solver-PUMI interactions.
-If the ownership is not provided, the default is set to $NULL$.
-If the ownership is $NULL$, the PUMI's default ownership rule is used (a part with the minimum process rank is the owning part of duplicate copies).
+Given a mesh, an ownership handle, and a field shape handle, initialize MSI services for solver-PUMI interactions.
+The ownership and field shape are optional (default: $NULL$).
+Ownership rule determines the owner copy among duplicated mesh entity copies by partitioning or ghosting.
+If the ownership handle is $NULL$, the PUMI's default rule is used (a part with the minimum process rank is the owning part of duplicate copies).
+Field shape defines the node distribution where the coordinates and field values (DOF's) are stored.
+If the shape is \emph{NULL}, the field shape saved in mesh (returned by \texttt{pumi$\_$mesh$\_$getShape}) is used.
+If it is not \textit{NULL}, the field shape of the mesh is set to $s$.
+
+Combining ownership rule and field shape, local/global node numbering are generated.
+See PUMI User's Guide for more information on ownership rule, field shape and numberings.
 
@@
 \begin{verbatim}
-int msi_scorec_finalize()
+int msi_finalize()
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Mesh Entity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In terms of mesh entity operation, MSI provides the operations only related to field ID of individual mesh entity as those are not supported in PUMI.
-For the rest of mesh entity operations including setting/getting field data (DOF) over nodes, use the API's in \texttt{PUMI.h}.
-
-\begin{verbatim}
-void msi_ment_getFieldID (
-    pMeshEnt  /* in */  e, 
-    pField  /* in */  f, 
-    int  /* in */  i,
-    int*  /* out */  start_dof_id, 
-    int*  /* out */  end_dof_id_plus_one)
-\end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a mesh entity handle, field handle and the index of node $i$, return the starting local ID and the ending local ID plus one for field data (DOF) of $i^{th}$ node of the entity.
-
-\begin{verbatim}
-void msi_ment_getGlobalFieldID (
-    pMeshEnt  /* in */  e, 
-    pField  /* in */  f, 
-    int  /* in */  i,
-    int*  /* out */  start_dof_id, 
-    int*  /* out */  end_dof_id_plus_one)
-\end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a mesh entity handle, field handle and the index of node $i$, return the starting global ID and the ending global ID plus one for field data (DOF) of $i^{th}$ node of the mesh entity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Field}
@@
 
-In terms of PUMI field, the attributes include:
+The attributes of PUMI field are:
 \begin{itemize}
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given field name, the number of values per node ($nv$), the number of field data per value of node ($nd$), and a shape function, \emph{(i)} create a field for all nodes (owned, non-owned part boundary and ghost), \emph{(ii)} switch the memory space for field data to a contiguous array, and \emph{(iii)} initialize the field data.
+Given a mesh instance, field name, the number of values per node ($nv$), the number of field data per value of node ($nd$), and a shape function, \emph{(i)} create a field for all nodes (owned, non-owned part boundary and ghost), \emph{(ii)} switch the memory space for field data to a contiguous array, and \emph{(iii)} initialize the field data.
 The \emph{size}, the number of field data per node is \textit{nv}$*$\textit{nd}.
@@
 
-The field shape is optional and the default is \textit{NULL}. If it is \textit{NULL}, the field shape of the mesh is used (a field shape returned by \texttt{pumi$\_$mesh$\_$getShape}).
+The field shape is optional (default: \textit{NULL}). If it is \textit{NULL}, the field shape of the mesh is used (a field shape returned by \texttt{pumi$\_$mesh$\_$getShape}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Node}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{verbatim} 
+int msi_node_getID (
+    pMeshEnt  /* in */  e, 
+    int  /* in */  n)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a mesh entity handle and the index of node $n$, return local number of $n^{th}$ node of the mesh entity.
+
+\begin{verbatim}
+int msi_node_getGlobalID (
+    pMeshEnt  /* in */  e, 
+    int  /* in */  n)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a mesh entity handle and the index of node $n$, return global number of $n^{th}$ node of the mesh entity.
+The global numbering is based on the ownership handle provided in \texttt{msi$\_$start}.
+
+\begin{verbatim}
+void msi_node_setField (
+    pField  /* in */  f, 
+    pMeshEnt  /* in */  e, 
+    int  /* in */  n,
+    int  /* in */  size_dof, 
+    double*  /* in */  dof_data
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a field handle, a mesh entity handle, the index of node $n$, size of DOF data and a double array containing DOF data, set the field data (DOF) of $n^{th}$ node of the entity.
+
+\begin{verbatim}
+int msi_node_getField(
+    pField  /* in */  f, 
+    pMeshEnt  /* in */  e, 
+    int  /* in */  n,
+    double*  /* out */  dof_data)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a field handle, a mesh entity handle, the index of node $n$, fill the array \textit{dof$\_$data} with field data (DOF) of $n^{th}$ node of the entity.
+
+\begin{verbatim}
+void msi_node_getFieldID (
+    pField  /* in */  f, 
+    pMeshEnt  /* in */  e, 
+    int  /* in */  n,
+    int*  /* out */  start_dof_id, 
+    int*  /* out */  end_dof_id_plus_one)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a field handle, a mesh entity handle, and the index of node $n$, return the starting local ID and the ending local ID plus one for field data (DOF) of $n^{th}$ node of the entity.
+
+\begin{verbatim}
+void msi_ment_getGlobalFieldID (
+    pField  /* in */  f, 
+    pMeshEnt  /* in */  e, 
+    int  /* in */  n,
+    int*  /* out */  start_dof_id, 
+    int*  /* out */  end_dof_id_plus_one)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a field handle, a mesh entity handle, and the index of node $n$, return the starting global ID and the ending global ID plus one for field data (DOF) of $n^{th}$ node of the mesh entity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{PETSc Matrix and Solver}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{verbatim}
@@
 \end{verbatim}\vspace{-.5cm}\hspace{1cm}
-Given a matrix type and a field handle, create a matrix and return its handle.
-The matrix type indicates the purpose of the matrix: 0 for matrix-vector multiplication and 1 for solver.
-The input field handle is used to retrieve the numbering (row/column ID) for matrix manipulation.
-The status of matrix is \textit{MSI$\_$NOT$\_$FIXED} so the matrix values can be modified.
+Given matrix type (0 for matrix-vector multiplication, 1 for solver) and a field handle, create a matrix and return its handle.
+The input field handle is used to set up the matrix size  and row/column ID's.The initial status of matrix is \textit{MSI$\_$NOT$\_$FIXED} so the matrix values can be modified.
 
@@
 Given a matrix handle, delete the matrix.
+
+\begin{verbatim}
+pField msi_matrix_getField (pMatrix  /* in */  matrix)
+\end{verbatim}\vspace{-.5cm}\hspace{1cm}
+Given a matrix handle, return the field handle associated with the matrix.
 

### 2017-09-14 api/msi.cc

@@ -257,6 +257,12 @@ msi_matrix* msi_matrix_create(int matrix_type, pField f)
 #endif 
 }
 
+pField msi_matrix_getField(pMatrix mat)
+{
+  return mat->get_field();
+}
+
+
 //*******************************************************
 void msi_matrix_assemble(pMatrix mat) 
 //*******************************************************

### 2017-09-14 api/msi.h

@@ -28,7 +28,7 @@ void msi_finalize(pMesh m);
 
 // field creation with multiple variables
 pField msi_field_create (pMesh m, const char* /* in */ field_name, 
-                      int /*in*/ nv, int /*in*/ nd, pShape shape=NULL);
+                      int /*in*/ nv, int /*in*/ nd);
 int msi_field_getNumVal(pField f);
 int msi_field_getSize(pField f);
 
@@ -59,6 +59,8 @@ typedef msi_matrix* pMatrix;
 /** matrix and solver functions with PETSc */
 pMatrix msi_matrix_create(int matrix_type, pField f);
 void msi_matrix_delete(pMatrix mat);
+pField msi_matrix_getField(pMatrix mat);
+
 void msi_matrix_assemble(pMatrix mat);
 
 void msi_matrix_insert(pMatrix mat, int row, int column, int scalar_type, double* val);
@@ -68,9 +70,10 @@ void msi_matrix_addBlock(pMatrix mat, pMeshEnt elem, int rowVarIdx, int columnVa
 void msi_matrix_setBC(pMatrix mat, int row);
 void msi_matrix_setLaplaceBC (pMatrix mat, int row, int size, int* columns, double* values);
 
+void msi_matrix_multiply(pMatrix mat, pField inputvec, pField outputvec);
+
 void msi_matrix_solve(pMatrix mat, pField rhs, pField sol);
 int msi_matrix_getNumIter(pMatrix mat);
-void msi_matrix_multiply(pMatrix mat, pField inputvec, pField outputvec);
 
 // auxiliary
 void msi_matrix_write(pMatrix mat, const char* file_name, int start_index=0);

### 2017-09-14 openmpi-gcc4.4.5-real-config.sh

@@ -1,4 +1,5 @@
-PREFIX=/fasttmp/seol/openmpi-gcc4.4.5-install
+PREFIX=/lore/seol/openmpi-gcc4.4.5-install
+ZOLTAN_DIR=$PREFIX
 PETSC_DIR=/lore/seol/petsc-3.5.4
 PETSC_ARCH=real-openmpi1.6.5
 cmake .. \
@@ -10,7 +11,7 @@ cmake .. \
   -DCMAKE_Fortran_FLAGS="-fpic "\
   -DSCOREC_INCLUDE_DIR=$PREFIX/include \
   -DSCOREC_LIB_DIR=$PREFIX/lib \
-  -DZOLTAN_LIBRARY="$PREFIX/lib/libzoltan.a" \
+  -DZOLTAN_LIBRARY="$ZOLTAN_DIR/lib/libzoltan.a" \
   -DPARMETIS_LIBRARY="$PETSC_DIR/$PETSC_ARCH/lib/libparmetis.a" \
   -DMETIS_LIBRARY="$PETSC_DIR/$PETSC_ARCH/lib/libmetis.a" \
   -DENABLE_PETSC=ON \

### 2017-09-14 api/msi.h
fixing error in the prev commit

@@ -28,7 +28,7 @@ void msi_finalize(pMesh m);
 
 // field creation with multiple variables
 pField msi_field_create (pMesh m, const char* /* in */ field_name, 
-                      int /*in*/ nv, int /*in*/ nd);
+                      int /*in*/ nv, int /*in*/ nd, pShape shape=NULL);
 int msi_field_getNumVal(pField f);
 int msi_field_getSize(pField f);
 
